---
title: "Tick Maxent Workflow"
author: "Craig"
date: "February 9, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Installing Necessary Packages

```{r}
library(dismo)
library(ENMeval)
library(latticeExtra)
library(maptools)
library(maps)
library(MaxentVariableSelection) #Used for SWD occurance data
library(tidyverse)
library(rasterVis)
library(raster)
library(rgdal)
library(rJava)
library(sf)
library(sp)
library(tictoc)
library(tmap)


```

##Loading Presence Points
1.  Import Data
2.  Select Random Training Points from Data
3.  Select 1-Random Training Points to get Testing Points
```{r}
occ <- read.csv(choose.files())
#longlat <- occ[,c(2,3)] #create data of just the lat long points, this is used to extract the datapoints from rasters.


```



##Loading Environmental Data
```{r}
files <- list.files("H:/Tick Project/SWD_Annual/Layers/", pattern='.asc', full.names = TRUE)

raster_variables <- raster::stack(files)


```


##Wrangling Data
1.  Make sure all data is in the same projection
2.  Make sure all data is in the same resolution
3.  Setting Same Extent

3.  SF can do this


##Select Background Points
1.  KFold Random Sampling
2.  Save as CSV


##Creating Presence and Background Points with Data
1.  Stack Raster Files
2.  Extract using the long/lat of presence points.  Can also extract by mask if using buffers.
3.  Create a new dataframe
4.  Use Extract to extract the rasterstack data based on the points

Questions:  How to subset the stack by month.  Either have a folder for each month, or use the subset()

```{r}
variables <- raster::stack(files)#stack rasters you want for SWD, need to match monthly models with the month of interest.  Either divide 

variables_at_occurance <- raster::extract(variables, longlat, method = 'simple') #can also do bilinear, this is using point data.  Can also use spatialpolygons

occ_swd <- as.data.frame(cbind("Ixodes pacificus", 
                               longlat,
                               variables_at_occurance))

occ_swd <- read.csv(choose.files()) # This is just for the test comparison where I am using Andy's already extracted dataset

Background <- read.csv(choose.files()) #this if just for the test using Andy's background points
Occurance <- read.csv(choose.files())
Predictors <- raster_variables #the raster files

Background <- Background %>% 
  select(aet, cwd, ppt, pptdjf, tmn, tmx, tmxjja, fvegrec, mam, brd, rep)

Occurance <- Occurance%>% 
  select(aet, cwd, ppt, pptdjf, tmn, tmx, tmxjja, fvegrec, mam, brd, rep)


swd <- rbind(Occurance, Background)
p <- c(rep(1,1592), rep(0,18000))
swd$fvegrec <- as.factor(swd$fvegrec)
```


##Running Maxent
1.  Subset to Month
2.  Run Maxent
3.  Predict/Project with Future
4.  Evaluate


Simple Maxent SWD, no additional arguments
```{r}
#tic()
#jar <- paste(system.file(package="dismo"), "/java/maxent.jar", sep='')
#if (file.exists(jar)){

 #     plot(ann_max_nojja)
#} else{
 # cat('cannot run this example because maxent is not available')
#  plot(1)
#}
#toc()

#ann_max_nojja

#, args=c("responsecurves=true", "jackknife=true", "maximumbackground=18000", "replicates=5", "maximumiterations=100")



tune_18_02_24_v07 <- maxent(x = swd, p = p, path="H:/Google Drive/Tick Project/RScriptTesting/SWD_Annual_nopptjja_Tuning/Results/tune_18_02_24_v07" ,args=c("responsecurves=true", "jackknife=true", "replicates=5", "maximumbackground=18000", "threshold=false", "hinge=false", "autofeature=false", "maximumiterations=10000"))

tune_18_02_24_v07

response(tune_18_02_24_v07)
```



```{r}


jar <- paste(system.file(package="dismo"), "/java/maxent.jar", sep='')
if (file.exists(jar)){
  ann_max_nojja <- maxent(x = swd, p = p, factors = raster_variables$fvegrec, progress ='text', args=c("responsecurves = true", "jackknife = true", "replicates = 5", "responsecurves = true", "nodata = -9999"))
      plot(ann_max_nojja)
} else{
  cat('cannot run this example because maxent is not available')
  plot(1)
}

if (file.exists(jar)) {
  response(ann_max_nojja)
} else {
  cat('cannot run this example beacuase maxent is not available')
  plot(1)
}

if (file.exists(jar)) {
  e <- evaluate(pres_testMax, back_testMax, xmJan, RasterStackMax)
  e
  
  px <- predict(ann_max_nojja, raster_variables, progress='text')
  par(mfrow=c(1,2))
  plot(px, main='Maxent, raw values NLCD')
  plot(counties, add=TRUE, border='dark grey')
  tr <- threshold(e, 'spec_sens')
  plot(px > tr, main='presence/absence Jan')
  plot(counties, add=TRUE, border='dark grey')
  points(pres_trainMax, pch='+')
} else {
  plot(1)}

xmNLCD

```


